---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TESTPKG)
```

# Function One - mybin()

This function takes the number of iterations (iter), the sample size (n), probability (p), and a boolean (ret). The boolean, ret, is used to signify whether you would prefer you would like extra information output. It uses the parameters to simulates binomial sample and then return a histogram of the sample 

# Function Two - myclt()

This function takes in the number of columns and number of samples. Using these parameters it creates a matrix of random samples. The columns of this matrix is summed and then displayed in a histogram to demonstrate the central limit theorem.

# Function Three - mycyi()

This function takes in a sample distribution and return a 95 percent confidence interval.

# Function Four - myncurve()

This package uses the parameters to generate a normal curve, and then uses the parameter xt to shade the region below the curve from 0 to xt.
